Highlighting Disputed Claims on the Web

### 2009-10-27 papers/www_disputefinder/disputefinder.tex
Spell check

In the realm of News, Pew~\cite{pew-news} report that, while internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible. Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.

@@

Dispute Finder consists of a database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_clim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

@@

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users are not distracted by things that they would not consider to be disputed). We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims. More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.

@@

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. Their are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user may behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgable about), but disengaged when reading about topics that don't affect them (e.g. entertainment) or topics for 
\todo{Use interviews to get some actual observations here. These are just fillers.}

@@

We used several different methods to gain input from users. We performed three rounds of users studies, circulated a survey within a target group, and conducted a series of interviews. We discuss the conclusions of these studies throught the paper, and in a section at the end. These studies were intended to inform the design of Dispute Finder, rather than to validate it. The only way to conclusively demonstrate that Dispute Finder is useful would be for it to be adopted by many active users -- something that the current implementation is not mature enough to support.

@@

Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realise that they should check it on one of these services. Dispute Finder is designed to work together with fact checking sites. Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.

\subsection{Analysing News}

@@

News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader persective of the issue. Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overal slant of the article. A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.

@@

Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}. Tagging tools allow users to collectively catagorize information by associating it with a user-created set of tags. In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.

@@

One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it condradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical. Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims. Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.

Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims. The algorithm we use is a simple varient of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}. LLM simply reduces a sentence to a bag of lemmatized words, removes stopwords, checks for negations, and then looks at what the overlap is between the words in the two phrases. Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.

@@

When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web. Kolak and Schillit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}. MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news soures and blogs.

@@

Several authors have analysed trust on Wikipedia. WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. All these tools determine trustworthiness by examining the edit history of a page.

@@

If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view. We could have ommitted this feature and still had a useful system. Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim. There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:

@@

Another point in favor of using a simple list of sources is that most of the users we talked to seemed to be more interested in {\it who} disputed a claim, rather than what their argument was. For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with. Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they prefered to read whichever article seemed to be most credible, rather than browsing an argumentation graph.

It is possible that the best solution would be a visualisation that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.

@@

There is a difficult trade-off here. If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own worldview then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against. On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right. If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously. We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.

@@

The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowdsourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

@@

Given a web page, Dispute Finder needs to indentify which snippets are making known disputed claims. We implemented and tested four different approaches:

@@

Explicit page marking has the highest accuracy, but the poorest coverage. Since a user is looking at the page in its entirity, they can read the snippet in context and make a good judgement about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also foundf that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

@@

A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing. The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be pratical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy. By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP. It divides the page into sentences, strips out stopwords, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scaccing the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

@@

For the first two studies, we recruited participants using Craigslist. We posted a message asking people to tell us how they used the web to form and promote their opinions, and used this to select people who we thought might fit our "skeptical reader" and "activist" personas. After these studies, we decided that the kind of person who looks for jobs of craigslist is unlikely to be a good fit for our personas, and so for the final study we instead used people we knew personally and thought fit our personas well. All study groups were small. The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had six participants participants (all male).

Each batch of users was shown a different iteration of the Dispute Finder design. The first two batches used versions in which users marked snippets explicitly, and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view. The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim. We present the findings of the three user studies together. Where a comment refers to particular version we make this clear.

Study sessions took approximately fourty five minutes. Participants were seated at a workstatation with the Firefox browser augemented with the Dispute Finder extension. They were asked to view pages that had highlighted claims on them, and to attempt to add new disputed claims to our database.

@@

\subsubsection{Findings}

@@

Most users were able to use Dispute Finder compentently as a skeptical reader (browsing information about disputed claims) but found it harder to act compentently as an activist (adding new disputed claims). Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims ("I want to see it work before I add stuff").

When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed. Not all users realised that one could click on a disputed claim to bring up more information. Several users complained about Dispute Finder highlighing snippets that weren't making the claim Dispute Finder indicated.

@@

Several users expressed confusion about how specific a claim they created should be. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information? In order to make a good judgement, one needs to know the range of similar claims that are being made by other web sites, and what claims there is good evidence against. If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.

@@

In the first two studies, the popup interface for a claim showed an argumentation graph. This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles. When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected. One user said "I can see myself getting addicted to this", and another said "it's very intuitivet".

Users seemed to have difficulty creating such graph structures however. Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim. For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems". Users correctly realised that the claims were related, but were not sure how best to connect them. Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.

@@

Several users created claims that had ambiguous meanings. One user entered a disputed claim about "Wood", meaning the guitarist "Ronnie Wood" of the Rolling Stones. Similar problems occured with claims that were specific to a particular country, or a particular point in time.

@@

Most users were frustrated by the relatively poor accuracy and recall that Dispute Finder has at present. Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder didn't highlight anything. Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated. If Dispute Finder is to be adopted widely then we will need to significantly improve precission and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.

\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}

>>>>

In the realm of News, Pew~\cite{pew-news} report that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible. Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.

@@

Dispute Finder consists of a database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

@@

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users are not distracted by things that they would not consider to be disputed). We currently use a combination of crowd-sourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims. More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.

@@

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. Their are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user may behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that don't affect them (e.g. entertainment) or topics for 
\todo{Use interviews to get some actual observations here. These are just fillers.}

@@

We used several different methods to gain input from users. We performed three rounds of users studies, circulated a survey within a target group, and conducted a series of interviews. We discuss the conclusions of these studies throughout the paper, and in a section at the end. These studies were intended to inform the design of Dispute Finder, rather than to validate it. The only way to conclusively demonstrate that Dispute Finder is useful would be for it to be adopted by many active users -- something that the current implementation is not mature enough to support.

@@

Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services. Dispute Finder is designed to work together with fact checking sites. Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.

\subsection{Analyzing News}

@@

News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overall slant of the article. A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.

@@

Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}. Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags. In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.

@@

One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it contradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical. Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims. Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.

Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims. The algorithm we use is a simple variant of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}. LLM simply reduces a sentence to a bag of lemmatized words, removes stop-words, checks for negations, and then looks at what the overlap is between the words in the two phrases. Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.

@@

When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web. Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}. MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news sources and blogs.

@@

Several authors have analyzed trust on Wikipedia. WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. All these tools determine trustworthiness by examining the edit history of a page.

@@

If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view. We could have omitted this feature and still had a useful system. Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim. There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:

@@

Another point in favor of using a simple list of sources is that most of the users we talked to seemed to be more interested in {\it who} disputed a claim, rather than what their argument was. For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with. Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they preferred to read whichever article seemed to be most credible, rather than browsing an argumentation graph.

It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.

@@

There is a difficult trade-off here. If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own world-view then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against. On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right. If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously. We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.

@@

The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

@@

Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims. We implemented and tested four different approaches:

@@

Explicit page marking has the highest accuracy, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

@@

A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing. The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy. By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP. It divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

@@

For the first two studies, we recruited participants using Craigslist. We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our "skeptical reader" and "activist" personas. After these studies, we decided that the kind of person who looks for jobs of Craigslist is typically not a good fit for our personas, and so for the final study we instead used people we knew personally and thought fit our personas well. All study groups were small. The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had six participants participants (all male).

Each batch of users was shown a different iteration of the Dispute Finder design. The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view. The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim. We present the findings of the three user studies together. Where a comment refers to particular version we make this clear.

Study sessions took approximately forty five minutes. Participants were seated at a workstation with the Firefox browser augmented with the Dispute Finder extension. They were asked to view pages that had highlighted claims on them, and to attempt to add new disputed claims to our database.

@@

\subsection{Findings}

@@

Most users were able to use Dispute Finder competently as a skeptical reader (browsing information about disputed claims) but found it harder to act competently as an activist (adding new disputed claims). Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims ("I want to see it work before I add stuff").

When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed. Not all users realized that one could click on a disputed claim to bring up more information. Several users complained about Dispute Finder highlighting snippets that weren't making the claim Dispute Finder indicated.

@@

Several users expressed confusion about how specific a claim they created should be. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information? In order to make a good judgment, one needs to know the range of similar claims that are being made by other web sites, and what claims there is good evidence against. If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.

@@

In the first two studies, the popup interface for a claim showed an argumentation graph. This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles. When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected. One user said "I can see myself getting addicted to this", and another said "it's very intuitive".

Users seemed to have difficulty creating such graph structures however. Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim. For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems". Users correctly realized that the claims were related, but were not sure how best to connect them. Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.

@@

Several users created claims that had ambiguous meanings. One user entered a disputed claim about "Wood", meaning the guitarist "Ronnie Wood" of the Rolling Stones. Similar problems occurred with claims that were specific to a particular country, or a particular point in time.

@@

Most users were frustrated by the relatively poor accuracy and recall that Dispute Finder has at present. Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder didn't highlight anything. Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated. If Dispute Finder is to be adopted widely then we will need to significantly improve precision and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.

\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"opposes" graph.}
